Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex
Corrected the order of bibitems to match IEEE standards

The central base station is the point of contact between the sensor network and the server. The data gathered by the Arduino Fio sensors are routed to the base station via XBee radios. The base station, which is itself a Raspberry Pi (see figure \ref{fig:base station}, forwards the data to the ACMx server using HTTP requests. Forwarding data is the main function of the base station.The base station runs the Raspbian operating system \cite{raspbian}, a lightweight version of Linux. Raspbian is optimized for the Raspberry Pi, so writing Python scripts that take care of forwarding the data via HTTP to the server was simple. The more difficult task was writing code to allow the base station Raspberry Pi to interface with the XBee radio, and listen for packets coming from the XBee attached to the Arduino Fio. The Python code that runs on the base station Raspberry Pi is listed in Appendix 2. The base station is also equipped to receive images via the XBee radio, and forward this data to the server. However, the time constraints of the project did not allow us to finish the code on the image acquisition Raspberry Pis that sends the image data via XBees. Therefore, when testing, we simply connected the image acquisition Raspberry Pis to a WiFi internet connection, and POSTed directly to the server, using the RESTful web services already in place.

@@

OpenALPR is a relatively new open source ALPR system that is built on top of OpenCV (a computer vision framework), and the Tesseract OCR engine. Initial commits to the source code were made in December, 2013. Using such a new program can be more risky than going with an established leader in the market, but we found that OpenALPR offered just the type of functionality we were looking for \cite{openalpr}.

@@

\textbf{B. Intrada ALPR}
Intrada ALPR uses the SOAP protocol for exchanging information. To create SOAP requests, we used the \verb+SoapClient+ class available in PHP to create, send, and receive the output of our request.

@@

\bibitem{patel2012} C. Patel, A. Patel and D. Patel, ``Optical Character Recognition by Open Source OCR Tool Tesseract: A Case Study,'' \emph{Intl. Journal Computer Applications} vol. 55, no. 10, Oct. 2012.

>>>>

The central base station is the point of contact between the sensor network and the server. The data gathered by the Arduino Fio sensors are routed to the base station via XBee radios. The base station, which is itself a Raspberry Pi (see figure \ref{fig:basestation}, forwards the data to the ACMx server using HTTP requests. Forwarding data is the main function of the base station.The base station runs the Raspbian operating system \cite{raspbian}, a lightweight version of Linux. Raspbian is optimized for the Raspberry Pi, so writing Python scripts that take care of forwarding the data via HTTP to the server was simple. The more difficult task was writing code to allow the base station Raspberry Pi to interface with the XBee radio, and listen for packets coming from the XBee attached to the Arduino Fio. The Python code that runs on the base station Raspberry Pi is listed in Appendix 2. The base station is also equipped to receive images via the XBee radio, and forward this data to the server. However, the time constraints of the project did not allow us to finish the code on the image acquisition Raspberry Pis that sends the image data via XBees. Therefore, when testing, we simply connected the image acquisition Raspberry Pis to a WiFi internet connection, and POSTed directly to the server, using the RESTful web services already in place.

@@

OpenALPR is a relatively new open source ALPR system that is built on top of OpenCV (a computer vision framework), and the Tesseract OCR engine. Initial commits to the source code were made in December, 2013 \cite{trainocr}. Using such a new program can be more risky than going with an established leader in the market, but we found that OpenALPR offered just the type of functionality we were looking for \cite{openalpr}.

@@

\textbf{B. Intrada ALPR}
Intrada ALPR uses the SOAP protocol for exchanging information \cite{soapw3c}. To create SOAP requests, we used the \verb+SoapClient+ class available in PHP to create, send, and receive the output of our request.

@@
